Fractional Types

### 2019-11-23 fracGC/p.tex
On sec 7

There has been ample work on ancillae before us.  For example
\cite{PhysRevA.94.042337} explicitly represent the lifetime of
quantum wires, enable quantum wires to be recycled, leading
to more efficient circuits.  Interesting applications of
ancillae is in the recent paper~\cite{DBLP:journals/cal/ZhouB19}
on Quantum runtime assertions.  In section~\ref{sub:id}, we
already mentioned dynamic assertion of entanglement; they
also show how to provide (dynamic) assertions on classical
states, and testing of superposition states.  Our techniques
should combine with theirs to provide even more possibilities
for dynamic assertions. Ancilla management is a complex
business, and the verified circuit compiler
ReVerC~\cite{amy2017verified} goes to great pains to
ensure that ancilla are dealt with properly.  Both
QCL~\cite{omer2002procedural} and Quipper~\cite{Green:2013:QSQ:2491956.2462177}
also do automatic (but not certified) ancilla management during code
generation.  This remains an active area of research, as
outlined in the CACM paper~\cite{valiron2015programming}.

@@

Another different thread of work stems from categorical models
of quantum computation, especially those based on dagger
compact closed categories as introduced
in~\cite{Abramsky:2004:CSQ:1018438.1021878}, and greatly
expanded upon in~\cite{abramsky2009categorical}.  Various
results can be obtained in that general setting, such as the
no-cloning theorem~\cite{abramsky2009no}. The $2016$ book
\cite{chiribella2016quantum} is a good survey of the
developments since. Selinger~\cite{selinger2007dagger,Selinger:2011:FDH:1942319.1942398}
has been particularly active in this area. Of particular
note for our applications are two 2005 papers by Abramsky
\cite{abramsky2005structural,dblp:conf/calco/abramsky05}
with explicit examples of circuits using trace that are very useful tests
for our approach.

>>>>

There has been ample work on ancillae before us.  For example
\cite{PhysRevA.94.042337} explicitly represents the lifetime of
quantum wires, enabling quantum wires to be recycled, leading
to more efficient circuits.  Interesting applications of
ancillae is in the recent paper~\cite{DBLP:journals/cal/ZhouB19}
on Quantum runtime assertions.  In section~\ref{sub:id}, we
already mentioned dynamic assertion of entanglement; they
also show how to provide (dynamic) assertions on classical
states, and testing of superposition states.  Our techniques
should combine with theirs to provide even more possibilities
for dynamic assertions. Ancilla management is a complex
business, and the verified circuit compiler
ReVerC~\cite{amy2017verified} goes to great pains to
ensure that ancilla are dealt with properly.  Both
QCL~\cite{omer2002procedural} and Quipper~\cite{Green:2013:QSQ:2491956.2462177}
also do automatic (but not certified) ancilla management during code
generation.  This remains an active area of research, as
outlined in the CACM paper~\cite{valiron2015programming}.

@@

Another different thread of work stems from categorical models
of quantum computation, especially those based on dagger
compact closed categories as introduced
in~\cite{Abramsky:2004:CSQ:1018438.1021878}, and greatly
expanded upon in~\cite{abramsky2009categorical}, or more
recently in~\cite{DBLP:conf/lics/HuotS19}. Various
results can be obtained in that general setting, such as the
no-cloning theorem~\cite{abramsky2009no}. The $2016$ book
\cite{chiribella2016quantum} is a good survey of the
developments since. Selinger~\cite{selinger2007dagger,Selinger:2011:FDH:1942319.1942398}
has been particularly active in this area. Of particular
note for our applications are two 2005 papers by Abramsky
\cite{abramsky2005structural,dblp:conf/calco/abramsky05}
with explicit examples of circuits using trace that are very useful tests
for our approach.
